---
title: "Firm Cascades"
---

## Firm Cascades


We will try to simulate firm cascades mainly in four different ways. 
Ideally, we need to have firm level data to calibrate our simulation.
We lack that data


### Cascades in Cross-hoolding Ownership networks

Assume three four firms. Asset and liabilities are interrelated. 
Each firm has a market value.

Let's call these firms, Firm1, Firm2, Firm3 and Firm4.
First we assign market values to each and assign an asset-liability matrix.

```{r setupFirm}
n <-4
names <- c("Firm1", "Firm2","Firm3","Firm4")
MV <- c(100, 400, 600, 1000) # the market values of the firms respectively
MV_new <- c(100, 200, 600, 1000)
C_raw <- matrix(c(0, 50, 100, 400,  100, 0, 300, 500, 200, 50, 0, 400, 40, 100, 500, 0), ncol = n, byrow = T)
C_raw
c <- 0.7
C <- c * C_raw %*% diag(1 / colSums(C_raw))
C

Chat <- (1 - c) * diag(n)

A <- Chat %*% solve(diag(n) - C)
A

theta <- 0.9

v_threshold <- theta * (A %*% MV)

all_failure_indicator <- rep(0, n)

pcurrent <- MV_new
```


In order to see the effect of the drop of market value of the Firm 2, we trace the cascade effects

```{r loop}
for (wave in 1:2)  {
  #wave <- wave + 1
  new_failure_indicator <- as.numeric((A %*% pcurrent) < v_threshold & all_failure_indicator == 0)
  
  all_failure_indicator <- pmax(all_failure_indicator, new_failure_indicator)
  # All failures to date
  
  pcurrent <- pcurrent - new_failure_indicator * v_threshold / 2
  
  new_failed_firms <- which(new_failure_indicator == 1)
  
  new_failed_names <- names[new_failed_firms]
  
  if (length(new_failed_firms) > 0) {
    cat('Wave', wave, 'failures are:\n')
    cat(toString(new_failed_names))
    cat('\n')
  }
  
}

```



Thus, a medium sized firm, having lost half of its market value,  will cause the whole firm network to collapse.


## Trade Credit Cascades




## Supply Chain Cascades



